A dynamic programming algorithm to assess the reliability of inferences from network enrichment analysis

### 2018-05-03 doc/genesetdp.tex
text

Since these methods of network randomization are not completely random, they introduce bias in the statistics that may or may not be desired, as the set of random networks is much larger than the ones of random networks that retain a certain topological characteristic. And the somewhat inaccessible process of so randomising networks produces statistics that are equaly hard to interpret. FIXME: Should this be in the dicussion?

@@

We implemented a Python program that read network and pathway definition files and scored query sets according to Equation \ref{eq:sum_i}, the Dynamic Programming algorithm described in the Algorithm section, that enabled us to assign $p$~values according to Equation \ref{eq:pval}. We downloaded pathway and network definitions from the BinoX's website and used the same network threshold as BinoX default ($0.7$).

@@

FIXME: What about:

>>>>

Since these methods of network randomization are not completely random, they introduce bias in the statistics that may or may not be desired, as the set of random networks is much larger than the ones of random networks that retain a certain topological characteristic. Also, the somewhat inaccessible process used to randomize networks produces statistics that are equaly hard to interpret as the null hypothesis becomes complex. FIXME: Should this be in the dicussion?

@@

We implemented a Python program that reads network and pathway definition files and scored query sets agains a pathway according to Equation \ref{eq:sum_i}, the Dynamic Programming algorithm described in the Algorithm section, that enabled us to assign $p$~values according to Equation \ref{eq:pval}. We downloaded pathway and network definitions from the BinoX's website and used the same network threshold as BinoX default ($0.7$).

@@
